\documentclass{article}
\title{Week 1, Stand-up 2}
\author{Jared Dyreson\\ California State University, Fullerton 
\and Mason Godfrey, California State University, Fullerton
\and Brian Lucero, California State University, Fullerton}

\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{Reports}

\subsection{Mason Godfrey}
\begin{enumerate}
\item This sprint, I fixed some logic behind our ant that made the ant move incorrectly on the y axis. I also fixed the fact that the ant was moving before updating the new square as opposed to updating the old square before moving, and commented code
\item Next, I plan to help my team members add animation to the ant
\item As of now, nothing is blocking further progress on the project
\end{enumerate}

\subsection{Jared Dyreson}
\begin{enumerate}
\item I have worked on improving the stability of the code we wrote, moved some constants to be encapsulated by the grid constructor and overall readability. I have also started working on comment headers to describe each function of each file and their respective authors
\item I plan to finish the Big O Analysis and move the position of the grid generation
\item There are no roadblocks in the foreseeable future
\end{enumerate}

\subsection{Brian Lucero}
\begin{enumerate}
\item Since the last standup report, I have put in some individual time to understand the logic behind the ant movements. Also, began researching into how I would be able to implement an animation for the actual ant. Realized that in order to implement the animation in a reasonable manner, the individual boxes for the grid would need to be increased in size and also more added to the grid overall. Consulted with Jared about how we can set up the current ant related functions right now so that we can achieve the ant animations.
\item I look forward to continuing to inquire more into those specific functions that way I can develop a list of possible avenues as far as ant animation.  Also determined that I need to research more into the logic of the program in general and prepare for some potential bugs that might occur with certain ant animation implementations. Will need to consult with Mason more about possible solutions and implementations to avoid for the functions he made. 
\item I don't see any reason why we wont be able to continue smoothly. No major roadblocks
\end{enumerate}
\end{document}
